---
title: "R_1"
author: "Jerome Mberia"
date: "1/9/2021"
output:
  html_document: default
  pdf_document: default
---


# Define the Question

## Specifying the Question
Which individuals are most likely to click on her ads?

## Defining the Metric for Success
Identify which individuals are most likely to click on her ads

## Understanding the context
A Kenyan entrepreneur has created an online cryptography course and would want to advertise it on her blog. She currently targets audiences originating from various countries.

## Recording the Experimental Design
1. Load , read and explore the dataset. 
2. Clean the dataset.
3. Perform Exploratory Data Analysis.
    * Univariate Analysis
    * Bivariate Analysis

## Data Relevance
This dataset is really usefull it contains details about the users that visit her blog.

# Dataset
```{r}
library(lubridate, warn.conflicts = FALSE)
```

```{r}
df<- read.csv('C:/Users/Admin/Downloads/advertising.csv')
head(df)
```

Number of columns
```{r}
ncol(df)
```

number of rows 
```{r}
nrow(df)
```
A summary of the datasets
```{r}
summary(df)
```

```{r}
head(df)
```


```{r}
tail(df)
```



```{r}
colnames(df)
```


```{r}
df$Timestamp <- ymd_hms(df$Timestamp)
```


```{r}
df$Male <- as.character(df$Male)
df$Male[df$Male == "0"] <- "Female"
df$Male[df$Male == "1"] <- "Male"
df$Male
```

```{r}
names(df)[names(df) == "Male"] <- "Gender"
```


```{r}
df$Clicked.on.Ad <- as.character(df$Clicked.on.Ad)
df$Clicked.on.Ad[df$Clicked.on.Ad == "0"] <- "No"
df$Clicked.on.Ad[df$Clicked.on.Ad == "1"] <- "Yes"
df$Clicked.on.Ad
```


```{r}
df$month <- month(df$Timestamp, label = TRUE)
df$month
```
 
```{r}
df$hour <- hour(df$Timestamp)
df$hour
```
 
 
```{r}
df$day.of.the.week <- wday(df$Timestamp, label = TRUE)
df$day.of.the.week
```

```{r}
head(df)
```


Univariate Analysis
Mean
Daily.Time.Spent.on.Site
```{r}
Daily_Time_1 <- mean(df$Daily.Time.Spent.on.Site)
Daily_Time_1
```

Age
```{r}
Age_3 <- mean(df$Age)
Age_3
```

Area.Income
```{r}
area_income_2 <- mean(df$Area.Income)
area_income_2
```

Daily.Internet.Usage
```{r}
Usage_2 <- mean(df$Daily.Internet.Usage)
Usage_2
```


Median
Daily.Time.Spent.on.Site
```{r}
Daily_Time <- median(df$Daily.Time.Spent.on.Site)
Daily_Time
```

Age
```{r}
Age_2 <- median(df$Age)
Age_2
```

Area.Income
```{r}
area_income_2 <- median(df$Area.Income)
area_income_2
```

Daily.Internet.Usage
```{r}
Usage_1 <- median(df$Daily.Internet.Usage)
Usage_1
```


Mode
```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
```
Age
```{r}
age_1 <- getmode(df$Age)
print(age_1)
```

Daily.Time.Spent.on.Site
```{r}
time_spent <- getmode(df$Daily.Time.Spent.on.Site)
print(time_spent)
```

Area.Income
```{r}
Income_1 <- getmode(df$Income)
print(Income_1)
```

Daily.Internet.Usage
```{r}
internet_usage <- getmode(df$Daily.Internet.Usage)
print(internet_usage)
```

Ad.Topic.Line
```{r}
topic_1 <- getmode(df$Ad.Topic.Line)
print(topic_1)
```

City
```{r}
city_1 <- getmode(df$City)
print(city_1)
```


Country
```{r}
country_1 <- getmode(df$Country)
print(country_1)
```

Gender
```{r}
gender_1 <- getmode(df$Gender)
print(gender_1)
```

Clicked.on.Ad
```{r}
clicked_1 <- getmode(df$Clicked.on.Ad)
print(clicked_1)
```

month
```{r}
month_1 <- getmode(df$month)
print(month)
```

day.of.the.week
```{r}
day_of_the_week <- getmode(df$day.of.the.week)
print(day_of_the_week)
```

hour
```{r}
hour_1 <- getmode(df$hour)
print(hour_1)
```


```{r}
result <- getmode(df$month)
print(result)
```




