---
title: "R_1"
author: "Jerome Mberia"
date: "1/9/2021"
output:
  html_document: default
  pdf_document: default
---


# Define the Question

## Specifying the Question
Which individuals are most likely to click on her ads?

## Defining the Metric for Success
Identify which individuals are most likely to click on her ads

## Understanding the context
A Kenyan entrepreneur has created an online cryptography course and would want to advertise it on her blog. She currently targets audiences originating from various countries.

## Recording the Experimental Design
1. Load , read and explore the dataset. 
2. Clean the dataset.
3. Perform Exploratory Data Analysis.
    * Univariate Analysis
    * Bivariate Analysis

## Data Relevance
This dataset is really usefull it contains details about the users that visit her blog.

# Dataset
```{r}
library(lubridate, warn.conflicts = FALSE)
```

```{r}
df<- read.csv('C:/Users/Admin/Downloads/advertising.csv')
df1 <- df
head(df)
```

## Number of columns
```{r}
ncol(df)
```

## number of rows 
```{r}
nrow(df)
```
## A summary of the datasets
```{r}
summary(df)
```
## Top six records in dataset
```{r}
head(df)
```

## Bottom six records in the dataset
```{r}
tail(df)
```


```{r}
colnames(df)
```
# Data Cleaning
## Duplicate 
```{r}
duplicated_rows <- df[duplicated(df),]
nrow(duplicated_rows)
```
```{r}
nrow(df)
df <- df[!duplicated(df), ]
nrow(df)
```
We didn't encounter any duplicate records in our dataset.

## Missing Values
```{r}
colSums(is.na(df))
```
We did encounter any missing value within dataset. 

## Outliers
```{r}
boxplot(df$Daily.Time.Spent.on.Site, main = "Daily Time Spent on Site")
boxplot(df$Age, main = 'Age')
boxplot(df$Area.Income, main = 'The User\'s Income')
boxplot(df$Daily.Internet.Usage, main = 'Daily Internet Usage')
```
### This are the are outliers in the column Area.Income
```{r}
boxplot.stats(df$Area.Income)$out
```

## Changing Timestamp column from a character column to a datetime column 
```{r}
df$Timestamp <- ymd_hms(df$Timestamp)
```

## Changing the column name
```{r}
names(df)[names(df) == "Male"] <- "Gender"
colnames(df)
```

## Changing the values from numbers to charaters 
```{r}
df$Gender <- as.character(df$Gender)
df$Gender[df$Gender == "0"] <- "Female"
df$Gender[df$Gender == "1"] <- "Male"
unique(df$Gender)
```

```{r}
df$Clicked.on.Ad <- as.character(df$Clicked.on.Ad)
df$Clicked.on.Ad[df$Clicked.on.Ad == "0"] <- "No"
df$Clicked.on.Ad[df$Clicked.on.Ad == "1"] <- "Yes"
unique(df$Clicked.on.Ad)
```

```{r}
#install.packages("devtools")

#devtools::install_github("tidyverse/lubridate")
```
```{r}
#library(lubridate, warn.conflicts = FALSE)
```


## Adding new column:
### month
```{r}
df$month <- month(df$Timestamp, label = TRUE)
df$month <- as.character(df$month)
unique(df$month)
```

### hour
```{r}
df$hour <- hour(df$Timestamp)
hours <- unique(df$hour)
sort(hours)
```
 
### Day of the week
```{r}
df$day.of.the.week <- wday(df$Timestamp, label = TRUE)
unique(df$day.of.the.week)
```

### date
```{r}
df$date <- date(df$Timestamp)
```


## Univariate Analysis
### Mean
#### Daily.Time.Spent.on.Site
```{r}
Daily_Time_1 <- mean(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
Daily_Time_1
```

#### Age
```{r}
Age_3 <- mean(df$Age[df$Clicked.on.Ad=="Yes"])
Age_3
```

#### Area.Income
```{r}
area_income_2 <- mean(df$Area.Income[df$Clicked.on.Ad=="Yes"])
area_income_2
```

#### Daily.Internet.Usage
```{r}
Usage_2 <- mean(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_2
```


### Median
#### Daily.Time.Spent.on.Site
```{r}
Daily_Time <- median(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
Daily_Time
```

#### Age
```{r}
Age_2 <- median(df$Age[df$Clicked.on.Ad=="Yes"])
Age_2
```

#### Area.Income
```{r}
area_income_2 <- median(df$Area.Income[df$Clicked.on.Ad=="Yes"])
area_income_2
```

#### Daily.Internet.Usage
```{r}
Usage_1 <- median(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_1
```


### Mode

```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
```

#### Age
```{r}
age_1 <- getmode(df$Age[df$Clicked.on.Ad=="Yes"])
print(age_1)
```

#### Daily.Time.Spent.on.Site
```{r}
time_spent <- getmode(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
print(time_spent)
```

#### Area.Income
```{r}
Income_1 <- getmode(df$Area.Income[df$Clicked.on.Ad=="Yes"])
print(Income_1)
```

#### Daily.Internet.Usage
```{r}
internet_usage <- getmode(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
print(internet_usage)
```

#### Ad.Topic.Line
```{r}
topic_1 <- getmode(df$Ad.Topic.Line[df$Clicked.on.Ad=="Yes"])
print(topic_1)
```

#### City
```{r}
city_1 <- getmode(df$City[df$Clicked.on.Ad=="Yes"])
print(city_1)
```


#### Country
```{r}
country_1 <- getmode(df$Country[df$Clicked.on.Ad=="Yes"])
print(country_1)
```

#### Gender
```{r}
gender_1 <- getmode(df$Gender[df$Clicked.on.Ad=="Yes"])
print(gender_1)
```

#### Clicked.on.Ad
```{r}
clicked_1 <- getmode(df$Clicked.on.Ad)
print(clicked_1)
```

#### month
```{r}
month_1 <- getmode(df$month[df$Clicked.on.Ad=="Yes"])
print(month_1)
```

#### day.of.the.week
```{r}
day_of_the_week <- getmode(df$day.of.the.week[df$Clicked.on.Ad=="Yes"])
print(day_of_the_week)
```

#### hour
```{r}
hour_1 <- getmode(df$hour[df$Clicked.on.Ad=="Yes"])
print(hour_1)
```

#### month
```{r}
result <- getmode(df$month[df$Clicked.on.Ad=="Yes"])
print(result)
```

### Maximum
#### Area.Income
```{r}
Income_2 <- max(df$Area.Income[df$Clicked.on.Ad=="Yes"])
print(Income_2)
```

#### Daily.Internet.Usage
```{r}
Usage_2 <- max(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_2
```

#### Daily.Time.Spent.on.Site
```{r}
time_spent_1 <- max(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
print(time_spent_1)
```

#### Age
```{r}
a_g_e <- max(df$Age[df$Clicked.on.Ad=="Yes"])
print(a_g_e)
```

### Minimum
#### Area.Income
```{r}
Income_3 <- min(df$Area.Income[df$Clicked.on.Ad=="Yes"])
print(Income_3)
```

#### Daily.Internet.Usage
```{r}
Usage_3 <- min(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_3
```

#### Daily.Time.Spent.on.Site
```{r}
time_spent_2 <- min(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
print(time_spent_2)
```

#### Age
```{r}
a_g_e_1 <- min(df$Age[df$Clicked.on.Ad=="Yes"])
print(a_g_e_1)
```

### Range
#### Area.Income
```{r}
Income_2 <- range(df$Area.Income[df$Clicked.on.Ad=="Yes"])
print(Income_2)
```

#### Daily.Internet.Usage
```{r}
Usage_2 <- range(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_2
```

#### Daily.Time.Spent.on.Site
```{r}
time_spent_1 <- range(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
print(time_spent_1)
```

#### Age
```{r}
a_g_e <- range(df$Age[df$Clicked.on.Ad=="Yes"])
print(a_g_e)
```

### Quantile
#### Area.Income
```{r}
Income_2 <- quantile(df$Area.Income[df$Clicked.on.Ad=="Yes"])
print(Income_2)
```

#### Daily.Internet.Usage
```{r}
Usage_2 <- quantile(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_2
```

#### Daily.Time.Spent.on.Site
```{r}
time_spent_1 <- quantile(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
print(time_spent_1)
```

#### Age
```{r}
a_g_e <- quantile(df$Age[df$Clicked.on.Ad=="Yes"])
print(a_g_e)
```

### Variance
#### Area.Income
```{r}
Income_2 <- var(df$Area.Income[df$Clicked.on.Ad=="Yes"])
print(Income_2)
```

#### Daily.Internet.Usage
```{r}
Usage_2 <- var(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_2
```

#### Daily.Time.Spent.on.Site
```{r}
time_spent_1 <- var(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
print(time_spent_1)
```

#### Age
```{r}
a_g_e <- var(df$Age[df$Clicked.on.Ad=="Yes"])
print(a_g_e)
```

### Standard Deviation
#### Area.Income
```{r}
Income_2 <- sd(df$Area.Income[df$Clicked.on.Ad=="Yes"])
print(Income_2)
```

#### Daily.Internet.Usage
```{r}
Usage_2 <- sd(df$Daily.Internet.Usage[df$Clicked.on.Ad=="Yes"])
Usage_2
```

#### Daily.Time.Spent.on.Site
```{r}
time_spent_1 <- sd(df$Daily.Time.Spent.on.Site[df$Clicked.on.Ad=="Yes"])
print(time_spent_1)
```

#### Age
```{r}
a_g_e <- sd(df$Age[df$Clicked.on.Ad=="Yes"])
print(a_g_e)
```



### Histogram
```{r}
hist_age <- df[df$Clicked.on.Ad == "Yes",]
# Create the histogram.
hist(hist_age$Age, main = "Age", xlab = "Age", col = "grey",border = "black")
```



```{r}
hist_age <- df[df$Clicked.on.Ad == "No",]
# Create the histogram.
hist(hist_age$Age, main = "Age", xlab = "Age", col = "grey",border = "black")
```

```{r}
hist_spent <- df[df$Clicked.on.Ad == "Yes",]
# Create the histogram.
hist(hist_spent$Daily.Time.Spent.on.Site, main = "Daily Time Spent on Site",  xlab = "Daily Time Spent on Site",col = "grey",border = "black")
```

```{r}
hist_spent <- df[df$Clicked.on.Ad == "No",]
# Create the histogram.
hist(hist_spent$Daily.Time.Spent.on.Site, main = "Daily Time Spent on Site",  xlab = "Daily Time Spent on Site",col = "grey",border = "black")
```

```{r}
hist_spent <- df[df$Clicked.on.Ad == "Yes",]
# Create the histogram.
hist(hist_spent$Area.Income, main = "User\'s Income",  xlab = "User\'s Income",col = "grey",border = "black")
```

```{r}
hist_spent <- df[df$Clicked.on.Ad == "No",]
# Create the histogram.
hist(hist_spent$Area.Income, main = "User\'s Income",  xlab = "User\'s Income",col = "grey",border = "black")
```
#### Analyisis:
1. Most people how spent less time on the site click on click of the ad while those how spent more time didn't click the ad.
2. Those with a income range around 50000 click on the ad while the those that didn't click most had high salary.

### Bivariate Analyisis
Note:
red: represents Yes
Blue: represents No

```{r}

df1

df1$Timestamp <- ymd_hms(df1$Timestamp)
names(df1)[names(df1) == "Male"] <- "Gender"
names(df1)[names(df1) == "Area.Income"] <- "Income"
names(df1)[names(df1) == "Daily.Internet.Usage"] <- "Usage"
names(df1)[names(df1) == "Daily.Time.Spent.on.Site"] <- "Spent"
df1$month <- month(df1$Timestamp)
df1$hour <- hour(df1$Timestamp)
df1$day.of.the.week <- wday(df1$Timestamp)
cor_df <- df1[, c('day.of.the.week', 'hour', 'month', 'Gender', 'Income', 'Spent', 'Usage', 'Age')]
#cor_df <- lapply(cor_df, as.numeric)
res <- cor(cor_df, cor_df)
round(res, 2)

```

```{r}
plot(df1$Spent, df1$Usage, main = "Main title",
     xlab = "X axis title", ylab = "Y axis title",
     pch = 19, frame = FALSE)
```

```{r}
plot(df1$Age, df1$Usage, main = "Age vs usage",
     xlab = "Age", ylab = "Usage",
     pch = 19, frame = FALSE)
```

```{r}

```


```{r}
colnames(df)
```


```{r}
# Alternatively, install just ggplot2:
# install.packages("ggplot2")

# Or the development version from GitHub:
# install.packages("devtools")

#devtools::install_github("tidyverse/ggplot2")
```

```{r}
library(ggplot2)
```

```{r}
a <- df[df$Clicked.on.Ad == "Yes",]
b = df[df$Clicked.on.Ad=="No",]
LGI_1 <- ggplot() + geom_line(aes(y=Daily.Time.Spent.on.Site, x=date), 
                            size=0.1, 
                            colour="red", 
                            data = a) +
  geom_line(aes(y=Daily.Time.Spent.on.Site, x=date), 
            size=0.1, 
            colour="blue", 
            data = b)

LGI_1
```

```{r}
LGI_1 <- ggplot() + geom_line(aes(y=Area.Income, x=date), 
                            size=0.1, 
                            colour="red", 
                            data = a) +
  geom_line(aes(y=Area.Income, x=date), 
            size=0.1, 
            colour="blue", 
            data = b)

LGI_1
```


```{r}

LGI_1 <- ggplot() + geom_line(aes(y=Daily.Internet.Usage, x=date), 
                            size=0.1, 
                            colour="red", 
                            data = a) +
  geom_line(aes(y=Daily.Internet.Usage, x=date), 
            size=0.1, 
            colour="blue", 
            data = b)

LGI_1
```

```{r}

LGI_1 <- ggplot() + geom_line(aes(y=Age, x=date), 
                            size=0.1, 
                            colour="red", 
                            data = a) +
  geom_line(aes(y=Age, x=date), 
            size=0.1, 
            colour="blue", 
            data = b)

LGI_1
```


### Analysis
Note:The analysis was consecrate on people who click on the ads
1. Most users spent 60 or less time on the site.
2. Most users have an income below 50000.
3. Most users use an internet usage of below 200
4. Most users are aged 40 or older.


# Conlusion:

1. People how spend 60 or less minutes on the site.
2. People how are 40 or older.
3. People living in the city of Lisamouth.
4. People living in the country of Czech Republic.
5. Target Females. 